Scattering of massless particles: scalars, gluons and gravitons

### 2024-07-22 test/main.tex
New

    \end{tikzpicture}
\end{frame}
\begin{frame}
    \frametitle{Trivalent graph expansion}
    \begin{alertblock}{Proposition}
        The function $m_n^{(0)}(\alpha|\beta)$ computes the sum of all trivalent scalar diagrams which can be regarded as both $\alpha$ color-ordered and $\beta$ color-orded.
    \end{alertblock}
    \pause
    More explicitly, 
    \begin{equation*}
        \boxed{m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}}
\end{equation*}
where the $\text{flip}(\alpha|\beta)$ is defined below, $\mathcal{T}(\alpha)$ and $\mathcal{T}(\beta)$ refer to the set of color-ordered diagrams in $\alpha$ and 
$\beta$ ordering respectively. To make this expression more clear, see the following diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{5.png}
\end{figure}
\end{frame}
\begin{frame}
    We take $m_8^{(0)}(I|18543762)$ as an example to explain how to compute it in an systematic way

@@

\end{frame}
\section{Summary and Outlook}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item A compact form of tree-level S-matrix in 3 different theories are introduced
            \begin{equation*}
                \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
             \end{equation*}
        \item The computaion method for double partial amplitudes are given 
            \begin{equation*}
                    m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}
            \end{equation*}
        \item The CK duality and BCJ double-copy relation can be easily obtained
            \begin{equation*}
                {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2,\quad e_{g_t}=\pm(e_{g_s}-e_{g_u})
            \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{The most general CHY form}
    In 2013, new formula for tree amplitudes of massless theories has been proposed by Cachazo, He and Yuan:
    \begin{equation*}
        \mathcal{A}=\boxed{\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)}\quad \mathcal{I}
    \end{equation*}
    \begin{itemize}
        \item Each particle is represented by a puncture in Riemann sphere.
        \item This form holds for general D-dimension.
        \item The boxed part is \alert{universial for all theories}.
        \item Only the integrand $\mathcal{I}$ determines the particular theory.
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{Connection between other theories}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{9.png}
    \end{figure}
\end{frame}
\begin{frame}
    \begin{figure}[t]
        \centering
        \includegraphics[width=1\linewidth]{4.png}
    \end{figure}
    \alert{arxiv: 1412.3479}
\end{frame}
\begin{frame}
    \centering
    \Huge Thanks for your attention!
\end{frame}
\appendix
\section{Appendix}

>>>>

    \end{tikzpicture}
\end{frame}
\begin{frame}
    \frametitle{Trivalent graph expansion}
    \begin{alertblock}{Proposition}
        The function $m_n^{(0)}(\alpha|\beta)$ computes the sum of all trivalent scalar diagrams which can be regarded as both $\alpha$ color-ordered and $\beta$ color-orded.
    \end{alertblock}
    \pause
    More explicitly, 
    \begin{equation*}
        \boxed{m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}}
\end{equation*}
where the $n_{\text{flip}}(\alpha|\beta)$ is defined below, $\mathcal{T}(\alpha)$ and $\mathcal{T}(\beta)$ refer to the set of color-ordered diagrams in $\alpha$ and 
$\beta$ ordering respectively. To make this expression more clear, see the following diagram
\begin{figure}[htb]
    \centering
    \includegraphics[width=0.8\linewidth]{5.png}
\end{figure}
\end{frame}
\begin{frame}
    I take $m_8^{(0)}(I|18543762)$ as an example to explain how to compute it in an tecnical way

@@

\end{frame}
\section{Summary and Outlook}
\begin{frame}
    \frametitle{Summary}
    \begin{itemize}
        \item A compact form of tree-level S-matrix in 3 different theories are introduced
            \begin{equation*}
                \mathcal{M}_n^{(s)}=\sum_{\alpha,\beta\in S_{n-2}}e_\alpha e_\beta m^{(0)}(\alpha|\beta)
             \end{equation*}
        \item The computaion method for double partial amplitudes are given 
            \begin{equation*}
                    m_n^{(0)}(\alpha|\beta)=(-1)^{n-3+n_{\text{flip}}(\alpha|\beta)}\sum_{g\in\mathcal{T}(\alpha)\cap\mathcal{T}(\beta)}\prod_{e\in E(g)}\frac{1}{s_e}
            \end{equation*}
        \item The CK duality and BCJ double-copy relation can be easily obtained
            \begin{equation*}
                {\cal M}^{(0)}_n\times{\cal M}^{(2)}_n={{\cal M}^{(1)}_n}^2,\quad e_{g_t}=\pm(e_{g_s}-e_{g_u})
            \end{equation*}
    \end{itemize}
\end{frame}
\begin{frame}
    \frametitle{The most general CHY form}
    In 2013, new formula for tree amplitudes of massless theories has been proposed by Cachazo, He and Yuan:
    \begin{equation*}
        \mathcal{A}=\boxed{\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)}\quad \mathcal{I}
    \end{equation*}
    \begin{itemize}
        \item Each particle is represented by a puncture in Riemann sphere.
        \item This form holds for general D-dimension.
        \item The boxed part is \alert{universial for all theories}.
        \item Only the integrand $\mathcal{I}$ determines the particular theory.
    \end{itemize}
\end{frame}
\begin{frame}
    \begin{figure}[t]
        \centering
        \includegraphics[width=1\linewidth]{4.png}
    \end{figure}
    \alert{arxiv: 1412.3479}
\end{frame}
\begin{frame}
    \frametitle{Connection between other theories}
    \begin{figure}
        \centering
        \includegraphics[width=0.8\linewidth]{9.png}
    \end{figure}
\end{frame}

\begin{frame}
    \centering
    \Huge Thanks for your attention!
\end{frame}
\appendix
\section{Appendix}
